---
title: "NBA Player Statistics"
output: html_notebook
---
#Importing the dataset
```{r}
season_stats <- read.csv("Seasons_Stats.csv")
View(season_stats)
```

#Choosing relevant data
This dataset has too many records and features, so we will choose the ones most relevant to what we need.
We'll be using the following columns:
* `Player`: Name of the player.    
 
 * `Pos`: Position of the player. It can be one of the following 5: PG, SG, SF, PF, C, or a combination of those.     
 
 * `Age`: Age of the player.    
 
 * `Tm`: Team of the player.  
 
 * `G`: Games played by the player on that season.     
 
 * `GS`: Games started by the player on that season, i.e., games where the player was on the starting line-up.  
 
 * `MPG`: Minutes Played per game.  
 
 * `PPG`: Points scored per game.  
 
 * `APG`: Assists made per game.   
 
 * `RPG`: Rebounds per game.   
 
 * `SPG`: Steals per game.
 
 * `BPG`:  Blocks per game.
 
 * `TOPG`: Turnovers per game.
 
 * `PFPG`:  Personal fouls per game.
 
 * `PER`:  Player Efficiency Rating (available since the 1951-52 season); PER is a rating developed by ESPN.com columnist John Hollinger. In John's words, "The PER sums up all a player's positive accomplishments, subtracts the negative accomplishments, and returns a per-minute rating of a player's performance."  
 
 * `TS.`: TS%, True Shooting Percentage, a measure of shooting efficiency that takes into account field goals, 3-point field goals, and free throws.   

<!-- *`X3PAr`:  3-Point Field Goal Attempts (available since the 1979-80 season in the NBA). -->
  
 * `USG.`: Usage Percentage (available since the 1977-78 season in the NBA). Usage percentage is an estimate of the percentage of team plays used by a player while he was on the floor.   
   
 * `WS`: an estimate of the number of wins contributed by a player.      
   
 * `VORP`: Value Over Replacement Player (available since the 1973-74 season in the NBA); a box score estimate of the points per 100 TEAM possessions that a player contributed above a replacement-level (-2.0) player, translated to an average team and prorated to an 82-game season   
   
 * `FG.`: Field Goal Percentage. 
 
 * `X2P.`: 2-Point Field Goal Percentage.  
 
 * `X3P.`: 3-Point Field Goal Percentage (available since the 1979-80 season in the NBA).   
 
 <!-- *`X3PA`: 3-Point Field Goal Attempts (available since the 1979-80 season in the NBA).      -->
```{r}

```

